MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-08-08 darmstadt_gscl_2013/article_twitter_normalization.tex
test data for noise cleaner added

Luckily for us, this ``novelty'' by Messina as well as @-tokens which
are in Twitter to mark names of user account both have strict formal
features by which these tokens could be identified. Other types of
words which are usually considered as OOVs and have unambiguous formal
traits are hyperlinks, e-mail addresses, and smileys. The presence of
such formal criteria suggests that these classes could best be handled
by rule-methods and namely finite-state techniques like finite-state
transducers (FST) (cf. Jurafsky and Martin, \cite{jurafsky},
pp.57-60).

@@

For hashtags, we simply stripped off the pound character from the
beginning of such words thus leaving only the alphabetic part of
tokens. A more complicated case turned out to be the @-tokens. For
them, we had to decide depending on the context whether these tokens
played an important syntactic role in sentence or not. In cases they
did, we additionally looked whether the alphabetic part following the
``@'' character was present in dictionary. If it was, we only stripped
the ``at'' character off, otherwise whole word was replaced with token
``\%UserName''. In cases when @-tokens served as addresses or retweet
marks, we deleted them from message since they were of little interest
and importance for further syntactic and semantic analysis and could
hardly be assigned a proper part-of-speech tag or syntactic role.

All the artificially introduced words were added to custom user
dictionaries of \texttt{TreeTagger} and \texttt{hunspell}. For
tagging, we assigned NE tags to all artificial words except for smiley
replacements which got the tag INJ. Additionally, positions and
lengths of all replacements we remembered along with original words
which were replaced and a restoration step to original forms was
performed for certain classes of tokens after tagging.

%
\subsection{Restoration of Umlauts}
%
\subsection{Squeezing of Elongated Words}
%
\subsection{Translation of Slang Idioms}
%
\section{Evaluation}\label{evaluation}

>>>>

Luckily for us, this ``novelty'' by Messina as well as @-tokens which
are used in Twitter to mark names of user account, both have strict
formal features by which these tokens could be identified. Other types
of words which are usually considered as OOVs and also have
unambiguous formal traits are hyperlinks, e-mail addresses, and
smileys. The presence of such formal criteria suggests that these
classes could best be handled by rule-methods and namely finite-state
techniques like finite-state transducers (FST) (cf. Jurafsky and
Martin, \cite{jurafsky}, pp.57-60).

@@

For hashtags, we simply stripped off the pound character from the
beginning of such words thus leaving only the alphabetic part of
tokens. A more complicated case turned out to be the @-tokens. For
them, we had to decide depending on the context whether these tokens
played an important syntactic role in sentence or not. In cases they
did, we additionally looked whether the alphabetic part following the
``@'' character was present in dictionary. If it was, we only stripped
the ``at'' character off, otherwise whole word was replaced with token
``\%UserName''. In cases when @-tokens served as addresses or retweet
marks, we deleted them from message completely since they were of
little interest and importance for further syntactic and semantic
analysis and could hardly be assigned a proper part-of-speech tag or
syntactic role.

All the artificially introduced words were added to custom user
dictionaries of \texttt{TreeTagger} and \texttt{hunspell}. For
tagging, we assigned NE tags to all artificial words except for
emoticon replacements which got the tag INJ. Additionally, positions
and lengths of all replacements we remembered along with original
words which were replaced and a restoration step to original forms was
performed for certain classes of tokens after tagging.

Precision, recall and F1 score for replacement of Twitter-specific
phenomena is shown in Table \ref{table:tw-phenomen-metrics}.

\begin{table}
  \caption{Precision, recall and F1 score for replacement of
    Twitter-specific phenomena\label{table:tw-phenomen-metrics}}
  \begin{tabular}{*{4}{>{\centering\arraybackslash}p{0.25\textwidth}}}
    \hline\noalign{\smallskip}
    OOV subclass & Precision & Recall & F1 score\\\hline
    @-tokens & 0 & 0 & 0\\
    hashtags & 0 & 0 & 0\\
    links & 0 & 0 & 0\\
    e-mail addresses & 0 & 0 & 0\\
    smileys & 0 & 0 & 0\\
    \noalign{\smallskip} \hline
  \end{tabular}
\end{table}

%
\subsection{Restoration of misspellings}
%
\subsubsection{Restoration of Umlauts}
%
\subsubsection{Squeezing of Elongated Words}
%
\subsubsection{Translation of Slang Misspellings}
%
\section{Evaluation}\label{evaluation}
